High-resolution ALMA observations of V4046\,Sgr: a circumbinary disc with a thin ring

### 2021-03-05 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

Interestingly, the ALMA image also detects faint 1.3\,mm continuum emission near the stellar positions (see the inset in Fig.~\ref{fig:images_vs_simulated}). Since this faint central emission is larger than the angular resolution, it is probably stemming from thermal emission from  large dust grains rather than directly from the stars. The main blob of this dust structure is at estimated distance of only $0\farcs012\pm0\farcs002$, or $\sim$0.85$\pm$0.14\,au from the binary system, and, estimating its form as a Gaussian ellipse, it has a mean FWHM of $\sim$1.43\,au. If this feature is caused by the presence of millimetre-sized dust, assuming optically thin emission, its estimated mass would be around 0.12\,M$_{\earth}$. %and may be part of an inner disc introduced in the RT model to match the SED (see Sec.~\ref{sec:model} below).

@@

The SED features the standard signature of a transition disk, with a distinctive “dip” in the continuum near 10 $\micron$m suggesting that small, warm dust is preferentially depleted (although not absent; see Section 4.2.1) near the central binary. although the very weak excess
in the near-infrared makes it clear that the dust optical depths
must be significantly diminished within at least a few AU of the
central stars*** \citep{Rosenfeld_2013}.

>>>>

Interestingly, the ALMA image also detects faint 1.3\,mm continuum emission near the stellar positions (see the inset in Fig.~\ref{fig:images_vs_simulated}). Since this faint central emission is larger than the angular resolution, it is probably stemming from thermal emission from  large dust grains rather than directly from the stars. The main blob of this dust structure is at estimated distance of only $0\farcs012\pm0\farcs002$, or $\sim$0.85$\pm$0.14\,au from the binary system, and, estimating its form as a Gaussian ellipse, it has a mean FWHM of $\sim$1.43\,au. If this feature is caused by the presence of millimetre-sized dust, assuming optically thin emission, its estimated mass would be around 0.12\,M$_{\earth}$.

\begin{multline}
      M_{blob} = 0.03 M_{\sun} \left(\frac{F}{1\,\mathrm{Jy}}\right) \left(\frac{D}{100\,\mathrm{pc}}\right)^2 \left(\frac{\lambda}{1.3\,\mathrm{mm}}\right)^3 
      \\
      \left(\frac{50\,\mathrm{K}}{T}\right)    \left(\frac{0.02\,\mathrm{cm^2/g}}{\kappa_{1.3\,\mathrm{mm}}}\right)
\end{multline}

@@

%The SED features the standard signature of a transition disk, with a distinctive “dip” in the continuum near 10 $\micron$m suggesting that small, warm dust is preferentially depleted (although not absent; see Section 4.2.1) near the central binary. although the very weak excess in the near-infrared makes it clear that the dust optical depths must be significantly diminished within at least a few AU of the central stars*** \citep{Rosenfeld_2013}.
